%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://mohammedshahid.com/}{\Large Mohammed Asir Shahid }} & \href{mailto:mohammedshahid@protonmail.com}{mohammedshahid@protonmail.com}\\
  %\href{http://mohammedshahid.com/}{http://www.mohammedshahid.com} 
  Selden, New York &  (516)-514-5047 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Stony Brook University}{Stony Brook, New York}
      {BS, Mathematics \& Applied Mathematics and Statistics}{Aug. 2017 -- Aug. 2020}
      \resumeItemListStart
        \resumeItem{GPA: }
          {3.80/4.00}
        \resumeItem{Dean's List: }
          {Fall 2017, Spring 2018, Fall 2018, Spring 2019, Fall 2019, Spring 2020}
	  \resumeItem{Recipient of a Presidential Scholarship (Full Tuition).}{}
        \resumeItem{Relevant Coursework: }
        {Data Analysis (Using R and Python), Statistical Laboratory (Using R and SAS), Computer Science Principles (Using Python), Introduction to Object Oriented Programming (Using Java).}
      \resumeItemListEnd

      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubItem{Crypto Trading Bot: }
    {Created a profitable crypto currency trading bot in Python using Coinbase's API. Working on further improving the bot using Machine Learning.}

    \resumeSubItem{Homelab: }
    {Home Server running several Virtual Machines with different services.}

    {Set up a server to run Nextcloud, Plex, VNC, and Nginx in order to create a web server and a media server.}

    \resumeSubItem{Data Analysis Project: }
    {Analyzed real world data with multiple predictors to find the best fitting model.}

    {Created a professional report in LaTeX explaining the findings of my analysis.}

  \resumeSubHeadingListEnd

%-----------CERTIFICATES-----------------
\section{Certificates}

  \resumeSubHeadingListStart

    \resumeSubheading
      {MITx MicroMasters}{}
      {Statistics and Data Science (General Track)}{May 2021 - Present}
      \resumeItemListStart
      \resumeItem{}
      {Graduate courses on Probability, Statistics, Data Analysis, and Machine Learning with Python.}
      \resumeItemListEnd

    \resumeSubheading
      {Dataquest}{}
      {Data Scientist in Python}{December 2020 - Present}
      \resumeItemListStart
      \resumeItem{}
      {Courses teaching Data Science and Visualization, SQL, Statistics, Machine Learning Models.}
      \resumeItemListEnd

    \resumeSubheading
      {Red Hat, Inc.}{}
      {Red Hat Certified System Administrator}{October 2021 (Expected)}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart


    \resumeSubheading
      {Stony Brook University Applied Mathematics Department}{Stony Brook, New York}
      {Teaching Assistant}{Aug. 2018 - December 2019}
      \resumeItemListStart
      \resumeItem{}
      {Teaching Assistant for Linear Algebra and Statistical Laboratory (Using R and SAS).}
      \resumeItem{}
      {Grading assignments and providing feedback to hundreds of students on tight deadlines as well as providing personal feedback regarding how they can improve.}
      \resumeItem{}
      {Demonstrating interpersonal skills by communicating effectively with my faculty adviser and my students.}
      \resumeItem{}
      {Holding office hours in order to host review sessions and instruct students with questions they have regarding the assignments and exams.}
      \resumeItemListEnd
    \resumeSubheading
      {Private Tutor}{Stony Brook, New York}
      {Tutor}{Aug. 2017 - Present}
      \resumeItemListStart
        \resumeItem{}
	{Teaching college level Computer Science and Mathematics (Statistics, Linear Algebra, Calculus, and Real Analysis) to fellow university students.}
        \resumeItem{}
          {Teaching Mathematics, Sciences, and Programming to students from Elementary School to High School.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    %\item{
    %  \textbf{Languages:}{ R, Python, LaTeX, SQL, Java, SAS}
    %}
    \item{
	 \textbf{Environment:} {Experience with Red Hat Enterprise Linux, Ubuntu, Debian, CentOS, OpenSUSE Leap, Gentoo Linux, NixOS, and Windows Server.}
    }
    \item{
        \textbf{Software Skills:} {Proficiency with Linux, System Administration, AWS, Azure, Google Cloud Platform, Docker, SQL Server, Shell Scripting, Virtualization, Microsoft Office Suite, and LaTeX.}
    }
    \item{
        \textbf{Programming Languages:} {Proficiency with R, Python, Octave, Bash, SQL, Java, C, C++, Lua.}
    }
    % \item{
    %     \textbf{Typing Speed:} {95 WPM.}
    % }

  \resumeSubHeadingListEnd

\end{document}
